The globular cluster system of the Auriga simulations

### 2019-06-14 AurigaGCS.tex
Intermediate version

% Rosenblatt+ 1988, Cen 2001, Bromm \& Clarke 2002, Diemand+ 2002, Moore+ 2006,
% Boley+ 2009, Griffen+ 2010, Trenti+ 2015, Kimm+ 2016, Ricotti+ 2016, Boylan-Kolchin 2017,
% Creasey+ 2019.

@@

% bimodality in the broad-band colours of many (perhaps most) GC systems (e.g.
% Zepf & Ashman 1993; Elson, Santiago & Gilmore 1996; Geisler,
% Lee & Kim 1996; Forbes, Brodie & Huchra 1997a; Gebhardt &
% Kissler-Patig 1999; Kundu & Whitmore 2001; Larsen et al. 2001).

@@

% \todo[inline]{
% TODO: paraphrase ``The diversity in morphological properties of these simulated
% galaxies reflects the stochasticity inherent to the process of galaxy formation
% and evolution
% \citep[e.g.][]{2005ApJ...635..931B, 2010MNRAS.406..744C, 2010ApJ...708.1398T}.''
% }
%
% \todo[inline]{Paragraph about Auriga's stellar haloes.
% ``The Auriga Stellar Haloes: Connecting stellar population properties with
% accretion and merging history'' \citet{2018arXiv180407798M}
% }

@@

\subsection{Milky Way}
\label{sec:milkyway}
\citet[][2010 edition; hereafter H96e10]{1996AJ....112.1487H} provides a
catalogue\footnote{See \url{https://www.physics.mcmaster.ca/Fac_Harris/mwgc.dat}}
of the Milky Way globular cluster system that contains properties of
157 GCs. The authors initially estimated the size of the MW GCS to be 180~$\pm$~10,
thus, their catalogue to be $\sim$85\% complete. However, an additional 59 GCs
are claimed to have been discovered by various authors. The total number of GCs
in the MW might add up to 216 with recent estimates now anticipating an additional 
thirty GCs yet to be discovered \citep[e.g.][and references therein]{2018ApJ...863L..38R}.
We still use data from the Harris catalogue, but caution that it may (only) be
53-72\% complete. Specifically, the relevant data fields that we use from H96e10
are the metallicity [Fe/H], the Galactic distance components $X$, $Y$, and $Z$ (in
kpc)\footnote{In a Sun-centered coordinate system: $X$ points toward Galactic
center, $Y$ in direction of Galactic rotation, and $Z$ toward the North Galactic
Pole. We calculate the galactocentric radius $R_{\text{GC}}=\sqrt{(X-R_\odot)^2
+ Y^2 + Z^2}$, assuming the solar radius $R_\odot=8$~kpc.}, and absolute
magnitude in the V-band $M_V$. We use the latter to calculate mass-estimates by
assuming $M_{V,\odot}=4.83$ and a mass to light ratio $M/L_V = 1.7$~M/L$_{\odot}$,
the mean for MW clusters \citep{2005ApJS..161..304M}.

@@

C11 and CR16 present a uniform set of spectroscopic observations calibrated
on the Milky Way GCS of the inner $1.6^\circ~(\sim21)$~kpc that
is believed to be 94\% complete. GCs in the outer stellar halo, up to
$R_{\text{proj}}\sim150$~kpc, are observed in the Pan-Andromeda Archaeological
Survey \citep[PAndAS, ][hereafter H14]{2014MNRAS.442.2165H}, but see also
\citet{2014MNRAS.442.2929V} and \citet{2019MNRAS.484.1756M}. H14 presents the
discovery of 59 new GCs and publishes updates to RBC~5. The work of H14 is
incorporated in the latest public release\footnote{Last revised 23 Sep 2015, see
\url{https://www.cfa.harvard.edu/oir/eg/m31clusters/M31_Hectospec.html}}
of the C11 dataset, further revised by CR16. It seems that CR16 is the most
recent aggregated dataset of M31's GCS that contains properties of interest
for our study as it contains GCs in the inner region and in the outer halo. The
relevant fields in the CR16 dataset that we use are the age, metallicity, and the
mass-estimate\footnote{The authors assumed $M/L_V = 2$ independent of [Fe/H]}.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{MW_M31_Age_Histogram-trim}.png}
    \caption{
        Age distribution of 55 GCs in the MW
        \citep[data from][]{2013ApJ...775..134V} and 88 GCs
        in M31 \citep[data from][]{2016ApJ...824...42C}.
        \label{fig:MW-M31-age}
    }
\end{figure}
% \begin{figure}
%     \includegraphics[width=\columnwidth]{{MW_M31_Age_HistogramMassWeighted_Msun}.png}
%     \caption{
%         Mass-weighted age distribution of 55 GCs in the MW
%         \citep[data from][]{2013ApJ...775..134V} and 85 GCs
%         in M31 \citep[data from][]{2016ApJ...824...42C}.
%         \label{fig:MW-M31-age}
%     }
% \end{figure}

\subsection{Total GC mass in metallicity-radial space}
\label{sec:observations_FeHRgc}
We show the two-dimensional mass-weighted metallicity-radial distribution of the
MW (M31) GCS in the top (bottom) panel of Figure~\ref{fig:observations_FeHRgc}. Both
quantities are readily available in H96e10 (assuming $R_{\odot}=8.0$~kpc), but
the galactocentric radius of GCs in M31 is not available in CR16. Therefore we
follow \citet[][Sec.~4.1]{2019arXiv190111229W} to calculate the projected radius
$R_{\text{proj}}$ from the observed positions, adopting M31's central position
from the NASA Extragalactic Database\footnote{\url{https://ned.ipac.caltech.edu/}}
$(\alpha_0, \, \delta_0) =
(0^{\text{h}}42^{\text{m}}44.35^{\text{s}}, \, +41^{\circ}16'08.63")$
and distance $D_{\text{M31}} = 778$~kpc (McConnachie et al. 2005; Conn  et  al. 2012).
We calculate $R_{\text{GC}}$ as `average deprojected distance`
$R_{\text{GC}} = R_{\text{proj}} \times (4/\pi)$. The observations indicate that
no GCs with high metallicities are to be expected at large radii (the three bins
in the upper right corner, both for MW and M31), and relatively few GCs at large
radii in general ($R_{\text{GC}} > 30$~kpc; right column: $11$ GCs or 7.3\% in
the MW and $17$ or 4.6\% in M31). We compare these observations to the Auriga
simulations later on in Sec.~\ref{sec:results_FeHRgc}.

@@

\begin{figure*}
    \includegraphics[width=\columnwidth]{{Au4-10_FeH_cleaner-trim}.png}
    \includegraphics[width=\columnwidth]{{Au4-4_and_Au4_21_FeH-trim}.png}
    \caption{
        \emph{Left:} Metallicity distribution of Au4-10 (bottom panel). We show
        the GG candicates in green. We split the GC candidates into two
        subpopulations, those that have formed insitu (blue), and those that have
        been accreted (red). The dotted green line shows all star particles.
        The solid purple (magenta) line in the top panel shows the GC system
        of the MW (M31). \emph{Right:} Au4-4 (bottom), and Au4-21 (top).
        \label{fig:Au4-10and21_FeH}
    }
\end{figure*}
Figure~\ref{fig:Au4-10and21_FeH} shows the normalized metallicity distribution
of \mbox{Au4-10}\footnote{The nomenclature is `Au' for Auriga, followed by the resolution
level (4) and halo number (10 - indicating which set of initial conditions was
used the run).} and \mbox{Au4-21}, showing the GC candidates in green. The accreted GC
candidates are shown in red, and the insitu subpopulation in blue. The top panels
show the MW (M31) GC system in purple (magenta). We overplot a double Gaussian
for the MW GCS (the purple dashed lines), adopting literature values of the
mean $\mu$ and standard deviation $\sigma$ of the metal-rich and metal-poor
populations \citep[][p. 38]{Harris2001}.

We find that the age cut lowers the mean metallicity from $0.0$ to $-0.6$.
Furthermore, the old accreted stars generally have lower metallicities than the
old insitu stars. The difference between the mean metallicity of the old insitu
and old accreted stars for the majority of the simulations is \textasciitilde{}$0.3$ (e.g.
\mbox{Au4-21}), and \textasciitilde{}$0.5$ dex for \mbox{Au4-10}, \mbox{Au4-16}, \mbox{Au4-17},
\mbox{Au4-18} and \mbox{Au4-22}. This trend is only reversed for \mbox{Au4-1}
and \mbox{Au4-4}, for which the old insitu population has a lower mean metallicity
instead. For \mbox{Au4-1} we find $\mu = -1.51$ (-0.74) for the old insitu (accreted),
but the former consists of only $1019$ particles ($1.3$\% of all GC candidates, and
with a total mass of 5e7 M\Sun) thus we believe our classification of insitu is
flawed for this halo due to misclassification of the primary halo in the merger
tree by subfind. For \mbox{Au4-4}, $10.8$ \% of the GC candidates is classified
as insitu (compared to insitu fractions of $40-80$\% for other haloes). Overall
we find that the simulations produce (sub)populations of GC candidates that are
more metal-rich than the MW and M31 GC systems. Moreover, none of the simulations
has a population of GC candidates with a bimodal metallicity distribution
(the green curves).

@@

We show the mean metallicity and standard deviation of all thirty Auriga L4 haloes
in Figure~\ref{fig:FeH_mu_sigma}. The green crosses are to be compared to the
purple (magenta) cross, which shows the mean value of all MW (M31) GCs.
We test the null hypothesis that MW (M31) and the GC candidates (all, insitu, and
accreted) are drawn from the same underlying distribution by calculating the KS
test statistic (i.e. six KS tests per simulation). We reject $H_0$ at the 100.00~\%
confidence level for virtually all subsets of all simulations, both for MW and M31,
except when comparing the old accreted stars of \mbox{Au4-10} to the MW GCS. In this
case we still reject $H_0$ with, but with $\leq 98.68$~\% confidence. When comparing
to the M31 GCS, the `best' matches are the old accreted subpopulations of \mbox{Au4-13},
\mbox{Au4-15}, and \mbox{Au4-17} ($H_0$ rejected with $\leq$ 99.82~\% confidence, 99.95~\%,
and 98.32~\%). Here we find that the cumulative distributions are more or less
similar up to [Fe/H]~$-0.5$, above which the simulations yield higher number
counts which drives the KS test statistic over the critical values. This affirms
our finding that the simulations produce GC candidates that are more metal-rich
than the MW (M31) GCS. The main reason reasons that $H_0$ is rejected with such
high confidence are under-production of old stars with [Fe/H]~$\leq$~-1.5,
and over-production of stars with [Fe/H]$\geq$~-0.5.

In addition, we show the metal-rich (metal-poor) population of the MW GCS using
a solid (open) dot. The mean metallicities of the old insitu populations appear
roughly consistent with that of the metal-rich population of the MW, but the
simulations show larger dispersions. We are uncertain whether definitive consensus
is reached concerning uni- or bimodality in the [Fe/H] distribution of M31, but
CR16 argues that the data, after removal of younger objects due to improved age
classification, leans towards unimodality. Therefore we do not show two data
points for the M31 GCS.

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMFeH_withRatios-trim}.png}
    \caption{
        Mass-weighted metallicity distribution of star particles in the Auriga
        simulations. We show the median value of all Auriga haloes for all
        stars (green dotted) and globular cluster candidates (i.e. stars with
        age $>$~10~Gyr; green solid). The latter sub set is further split up
        between stars that formed in-situ (blue solid), and those that were accreted
        (red solid). Shaded regions indicate the $1\sigma$ interval. The MW (M31)
        GCS is shown in purple (magenta). The middle (bottom) panel shows the
        ratio of the simulated mass to the mass in the MW (M31) GCS.
        \label{fig:FeH}
    }
\end{figure}
We now turn to the total mass in GC candidates produced by the Auriga simulations.
We show the median (coloured lines) for all thirty Auriga L4 haloes with the
$1\sigma$ interval around it (shaded regions, which shows the scatter between
runs that have different initial conditions, thus, have unique merger histories).
We chose to aggregate the data to indicate a general trend that we find when the
GC candidates are split up according to birth location, rather than selecting
typical examples of individual galaxies. Figure~\ref{fig:FeH} shows the mass-weighted
metallicity distribution of all Auriga L4 galaxies. Once again we notice that the
peak metallicity shifts down from $0$ to $-0.5$ for old stars (green solid)
compared to all stars (green dotted), and we learn that the mass at the peak
lowers by roughly one dex. The mass budget of the old stars is dominated by the
old insitu population (blue solid) below [Fe/H]~=~$-1$, and by the old accreted
stars (red solid) above this value. We show the MW (M31) GCS in purple (magenta)
and we show the ratio of the simulated to the observed profiles in the middle
(bottom) panel. This mass excess can be thought of the `mass budget' that the
Auriga GC candidates can `afford to lose' due to a combination of smaller than
unity bound cluster formation efficiencies combined with a Hubble time of dynamical
evolution, while still producing a GC system with sufficient mass to be consistent
with the MW (M31) GCS. The cluster formation efficiency would have to linearly
decrease with decreasing metallicity for Auriga GC candidates to produce a population
of GC candidates that is consistent with the MW. For the GC candidates in M31
we find a constant mass excess up to $-0.9$, above which the
simulations produce a higher mass excess with increasing metallicity. If dynamical
evolution is not expected to more efficiently disrupt GCs of higher metallicity,
then we would find that the efficiency to form bound star clusters would have to
decrease with increasing metallicity.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMRgc_withRatios-trim}.png}
    \caption{
        Mass-weighted radial distribution of star particles in the Auriga
        simulations. We show the median value of all Auriga haloes for all
        stars (green dotted) and globular cluster candidates (i.e. stars with
        age $>$~10~Gyr; green solid). The latter sub set is further split up
        between stars that formed in-situ (blue solid), and those that were accreted
        (red solid). Shaded regions indicate the $1\sigma$ interval. The MW (M31)
        GCS is shown in purple (magenta). The middle (bottom) panel shows the
        ratio of the simulated mass to the mass in the MW (M31) GCS.
        \label{fig:Rgc}
    }
\end{figure}
Figure~\ref{fig:Rgc} shows the mass-weighted radial distribution of the
Auriga L4 haloes. We notice a subtle peak around $10$~kpc for all star
particles that is not present for the GC candidates, indicating that the
stellar disc is no longer present when applying the latter selection criterion.
Furthermore, we find that the dominant contribution to the total mass in GC
candidates changes from those formed insitu to the accreted population around
$10$~kpc. Again we show the mass excess of the simulations compared to the Milky
Way and Andromeda GCS. We find a decreasing mass excess with increasing radius
in the range $0.2$ to \textasciitilde{}$5$ kpc, followed by an increase attributed
to the accreted subpopulation. We further investigate a breakdown of the total mass
in Auriga GC candidates into bins of both metallicity and radius in the following
section.

@@

\section{Discussion}
\label{sec:discussion}
\subsection{Metallicity distribution}
\label{sec:discussion_FeH}
We find that the metallicity distributions of GC candidates in the Auriga
simulations are more metal-rich than the MW (M31) GCS. Although the (old) star
particles represent single stellar populations with a mass (resolution) comparable
to the peak of the GCMF, they are in fact statistical tracers of the stellar
population of the galaxy as a whole. Therefore only a (small) fraction of the
star particles may represent plausible formation sites of GCs, whereas the majority
represent (halo) field stars - the disk component effectively falls outside
our selection of star particles due to the age cut. Globular clusters are
$\sim$~$0.5$ dex more metal-poor than spheroid stars observed at the same radius
for almost all galaxies \citep{1991ARA&A..29..543H}. Our finding that star particles older
than 10~Gyr have higher metallicities than the MW (M31) GCS may simply be a
reflection thereof.

\citet[][p. 234]{1998gcs..book.....A} and \citet[][p. 38]{Harris2001} quantify
the bimodality of the [Fe/H] distribution of the MW GCS, the latter fit a double
Gaussian which peaks at [Fe/H] = $-1.59$ (metal-poor) and $-0.51$ (metal-rich)
and dispersions of $0.34$ and $0.23$. However, the metallicity distribution of
GC candidates in the Auriga simulations is not bimodal, although an offset between
the mean values does emerge when further splitting them up according to birth location
(accreted or in-situ). The majority of the simulations show an offset in the mean
values of roughly $0.3$~dex between both subpopulations, while a small number of
simulations has an offset of order $0.5$~dex. Our finding that the mean values of
the old insitu GC candidates are roughly consistent with the metal-rich MW GCs
could be interpreted as an indication that this subpopulation may have formed
in-situ. However, we also notice that a substantial number of simulations has
similar mean values for all GC candidates, and the simulated insitu GC candidates
have larger dispersions than the metal-rich GCs. Moreover, the offset between the
mean of the metal-rich and metal-poor populations in the MW is $1$ dex, a factor
$2-3$ larger than the offset we find between the insitu and accreted populations.
The simulations are not consistent with the picture that all metal-rich GCs
formed insitu and that all metal-poor GCs were accreted.

\citet{2006ARA&A..44..193B} compare the number of metal-poor GCs to the stellar
halo mass and find\footnote{the quantity $T$ is the number of GCs per $10^9$ M\Sun \,
of galaxy stellar mass} $T^n_{\text{blue}} \sim 100$, while the
number of metal-rich GCs compared to the bulge mass yields $T^n_{\text{red}} \sim 5$,
and therefore conclude that the formation efficiency of metal-poor GCs is
twenty times higher than the metal-rich GCs with respect to field stars.

% Interestingly, the cross-over point above (below) which the mass-weighted
% metallicity distribution of GC candidates is dominated by those that have
% formed insitu (were accreted) coincides with the separation between the metal-rich
% and metal-poor population for the MW GCS at [Fe/H]~=~$-1$.

\subsection{Radial distribution}
\label{sec:discussion_Rgc}
The M31 GCS has a factor 2-3 more GCs at large radii compared to the MW GCS,
which may indicate that M31 has a richer merger history than the MW. In the
Auriga simulations we find that the GC candidates at radii larger than
$\sim20$~kpc are indeed dominated by accreted star particles. However, we select
star particles that are bound to the main halo and main subhalo, which means that
we include particles up to the virial radius $R_{200}$. The Auriga simulations
have no problem populating the stellar halo up to the virial radius, even with
our additional age cut. On the other hand, the MW and M31 have fewer GCs at large
radii. We expect tidal disruption to be less efficient at larger radii, thus,
the formation efficiencies of the accreted GC candidates would have to be lower.
Our classification as GC candidates could, for example, be improved by selecting
a number of globular clusters based on the $M_{vir}-N_{\text{GC}}$ correlation
found by \citet{2019arXiv190100900B}, and taking a virial mass below which none
of the star particles is treated as GC candidate.

>>>>

@@

@@

@@

\subsection{Milky Way}
\label{sec:milkyway}
\citet[][2010 edition; hereafter H96e10]{1996AJ....112.1487H} provides a
catalogue\footnote{See \url{https://www.physics.mcmaster.ca/Fac_Harris/mwgc.dat}}
of the Milky Way globular cluster system that contains properties of
157 GCs. The authors initially estimated the size of the MW GCS to be 180~$\pm$~10,
thus, their catalogue to be ${\sim}$85\% complete. However, an additional 59 GCs
are claimed to have been discovered by various authors. The total number of GCs
in the MW might add up to 216 with recent estimates now anticipating an additional 
thirty GCs yet to be discovered \citep[e.g.][and references therein]{2018ApJ...863L..38R}.
We still use data from the Harris catalogue, but caution that it may (only) be
53-72\% complete. Specifically, the relevant data fields that we use from H96e10
are the metallicity [Fe/H], the Galactic distance components $X$, $Y$, and $Z$ (in
kpc)\footnote{In a Sun-centered coordinate system: $X$ points toward Galactic
center, $Y$ in direction of Galactic rotation, and $Z$ toward the North Galactic
Pole. We calculate the galactocentric radius $R_{\text{GC}}=\sqrt{(X-R_\odot)^2
+ Y^2 + Z^2}$, assuming the solar radius $R_\odot=8$~kpc.}, and absolute
magnitude in the V-band $M_V$. We use the latter to calculate mass-estimates by
assuming $M_{V,\odot}=4.83$ and a mass to light ratio $M/L_V = 1.7$~M/L$_{\odot}$,
the mean for MW clusters \citep{2005ApJS..161..304M}.

@@

C11 and CR16 present a uniform set of spectroscopic observations calibrated
on the Milky Way GCS of the inner $1.6^\circ~({\sim}21)$~kpc that
is believed to be 94\% complete. GCs in the outer stellar halo, up to
$R_{\text{proj}}\sim150$~kpc, are observed in the Pan-Andromeda Archaeological
Survey \citep[PAndAS, ][hereafter H14]{2014MNRAS.442.2165H}, but see also
\citet{2014MNRAS.442.2929V} and \citet{2019MNRAS.484.1756M}. H14 presents the
discovery of 59 new GCs and publishes updates to RBC~5. The work of H14 is
incorporated in the latest public release\footnote{Last revised 23 Sep 2015, see
\url{https://www.cfa.harvard.edu/oir/eg/m31clusters/M31_Hectospec.html}}
of the C11 dataset, further revised by CR16. It seems that CR16 is the most
recent aggregated dataset of M31's GCS that contains properties of interest
for our study as it contains GCs in the inner region and in the outer halo. The
relevant fields in the CR16 dataset that we use are the age, metallicity, and the
mass-estimate\footnote{The authors assumed $M/L_V = 2$ independent of [Fe/H]}.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{MW_M31_Age_Histogram-trim}.png}
    \caption{
        Age distribution of 55 GCs in the MW
        \citep[data from][]{2013ApJ...775..134V} and 88 GCs
        in M31 \citep[data from][]{2016ApJ...824...42C}.
        \label{fig:MW-M31-age}
    }
\end{figure}

\subsection{Total GC mass in metallicity-radial space}
\label{sec:observations_FeHRgc}
We show the two-dimensional mass-weighted metallicity-radial distribution of the
MW (M31) GCS in the top (bottom) panel of Figure~\ref{fig:observations_FeHRgc}. Both
quantities are readily available in H96e10 (assuming $R_{\odot}=8.0$~kpc), but
the galactocentric radius of GCs in M31 is not available in CR16. Therefore we
follow \citet[][Sec.~4.1]{2019arXiv190111229W} to calculate the projected radius
$R_{\text{proj}}$ from the observed positions, adopting M31's central position
from the NASA Extragalactic Database\footnote{\url{https://ned.ipac.caltech.edu/}}
$(\alpha_0, \, \delta_0) =
(0^{\text{h}}42^{\text{m}}44.35^{\text{s}}, \, +41^{\circ}16'08.63")$
and distance $D_{\text{M31}} = 780$~kpc \citep{2005MNRAS.356..979M,2012ApJ...758...11C}
We calculate $R_{\text{GC}}$ as `average deprojected distance`
$R_{\text{GC}} = R_{\text{proj}} \times (4/\pi)$. The observations indicate that
no GCs with high metallicities are to be expected at large radii (the three bins
in the upper right corner, both for MW and M31), and relatively few GCs at large
radii in general ($R_{\text{GC}} > 30$~kpc; right column: $11$ GCs or 7.3\% in
the MW and $17$ or 4.6\% in M31). We compare these observations to the Auriga
simulations later on in Sec.~\ref{sec:results_FeHRgc}.

@@

\begin{figure*}
    \includegraphics[width=\columnwidth]{{Au4-10_FeH_cleaner-trim}.png}
    \includegraphics[width=\columnwidth]{{Au4-4_and_Au4_21_FeH-trim}.png}
    \caption{
        \emph{Left:} Metallicity distribution of Au4-10 (bottom panel). We show
        the GG candicates in green. We split the GC candidates into two
        subpopulations, those that have formed insitu (blue), and those that have
        been accreted (red). The dotted green line shows all star particles.
        The solid purple (magenta) line in the top panel shows the GC system
        of the MW (M31). \emph{Right:} Au4-4 (bottom), and Au4-21 (top).
        \label{fig:Au4-10and21_FeH}
    }
\end{figure*}
Figure~\ref{fig:Au4-10and21_FeH} shows the normalized metallicity distribution
of \mbox{Au4-10}\footnote{The nomenclature is `Au' for Auriga, followed by the
resolution level (4) and halo number (10, indicating which set of initial
conditions was used the run).}, \mbox{Au4-21}, and \mbox{Au4-4}, showing the GC
candidates in green. The accreted GC candidates are shown in red, and the insitu 
subpopulation in blue. The top panel of the left panel shows the MW (M31) GC 
system in purple (magenta). We overplot a double Gaussian for the MW GCS (the 
purple dashed lines), adopting literature values of the mean $\mu$ and standard
deviation $\sigma$ of the metal-rich and metal-poor populations \citep[][p. 38]{Harris2001}.

We find that the age cut, on average, lowers the mean metallicity from $0.0$ to $-0.5$.
Furthermore, the old accreted stars generally have lower metallicities than the
old insitu stars. The difference between the mean metallicity of the old insitu
and old accreted stars for the majority of the simulations is ${\sim}0.3$ (e.g.
\mbox{Au4-21}), and ${\sim}0.5$ dex for \mbox{Au4-10}, \mbox{Au4-16}, \mbox{Au4-17},
\mbox{Au4-18} and \mbox{Au4-22}. This trend is only reversed for \mbox{Au4-1}
and \mbox{Au4-4}, for which the old insitu population has a lower mean metallicity
instead. For \mbox{Au4-1} we find $\mu = -1.51 \, ({-0.74})$ for the old insitu (accreted),
but the former consists of only $1019$ particles ($1.3$\% of all GC candidates, and
with a total mass of 5e7 M\Sun) thus we believe our classification of insitu is
flawed for this halo due to misclassification of the primary halo in the merger
tree by subfind. For \mbox{Au4-4}, ${10.8}$\% of the GC candidates is classified
as insitu (compared to insitu fractions of ${40-80}$\% for other haloes). Overall
we find that the simulations produce (sub)populations of GC candidates that are
more metal-rich than the MW and M31 GC systems. Moreover, none of the simulations
has a population of GC candidates with a bimodal metallicity distribution
(the green curves).

@@

We show the mean metallicity and standard deviation of all thirty Auriga L4 haloes
in Figure~\ref{fig:FeH_mu_sigma}. The green crosses are to be compared to the
purple (magenta) cross, which shows the mean value of all MW (M31) GCs.
We test the null hypothesis that MW (M31) and the GC candidates (all, insitu, and
accreted) are drawn from the same underlying distribution by calculating the KS
test statistic (i.e. six KS tests per simulation). We reject $H_0$ at the 100.00~\%
confidence level for virtually all subsets of all simulations, both for MW and M31,
except when comparing the old accreted stars of \mbox{Au4-10} to the MW GCS. In this
case we still reject $H_0$ with, but with $\leq 98.68$~\% confidence. When comparing
to the M31 GCS, the `best' matches are the old accreted subpopulations of \mbox{Au4-13},
\mbox{Au4-15}, and \mbox{Au4-17} ($H_0$ rejected with $\leq$ 99.82~\% confidence, 99.95~\%,
and 98.32~\%). Here we find that the cumulative distributions are more or less
similar up to [Fe/H]~$-0.5$, above which the simulations yield higher number
counts which drives the KS test statistic over the critical values. This affirms
our finding that the simulations produce GC candidates that are more metal-rich
than the MW (M31) GCS. The main reasons that $H_0$ is rejected with such
high confidence are under-production of old stars with [Fe/H]~$\leq$~-1.5,
and over-production of stars with [Fe/H]$\geq$~-0.5.

In addition, we show the metal-rich (metal-poor) population of the MW GCS using
a solid (open) dot. The mean metallicities of the old insitu populations appear
roughly consistent with that of the metal-rich population of the MW, but the
simulations show larger dispersions. We are uncertain whether definitive consensus
is reached concerning uni- or bimodality in the [Fe/H] distribution of M31, but
CR16 argues that the data, after removal of younger objects due to improved age
classification, hints at three populations. However, we do not show these (unknown)
points for the M31 GCS.

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMFeH_withRatios-trim}.png}
    \caption{
        Mass-weighted metallicity distribution of star particles in the Auriga
        simulations. We show the median value of all Auriga haloes for all
        stars (green dotted) and globular cluster candidates (i.e. stars with
        age $>$~10~Gyr; green solid). The latter sub set is further split up
        between stars that formed in-situ (blue solid), and those that were accreted
        (red solid). Shaded regions indicate the $1\sigma$ interval. The MW (M31)
        GCS is shown in purple (magenta). The middle (bottom) panel shows the
        ratio of the simulated mass to the mass in the MW (M31) GCS.
        \label{fig:FeH}
    }
\end{figure}
We now turn to the total mass in GC candidates produced by the Auriga simulations.
We show the median (coloured lines) for all thirty Auriga L4 haloes with the
$1\sigma$ interval around it (shaded regions, which shows the scatter between
runs that have different initial conditions, thus, have unique merger histories).
We chose to aggregate the data to indicate a general trend that we find when the
GC candidates are split up according to birth location, rather than selecting
typical examples of individual (simulated) galaxies. Figure~\ref{fig:FeH} shows 
the mass-weighted metallicity distribution of all Auriga L4 galaxies. Once again 
we notice that the peak metallicity shifts down from $0$ to $-0.5$ for old stars
(green solid) compared to all stars (green dotted), and we learn that the mass at 
the peak lowers by roughly one dex. The mass budget of the old stars is dominated
by the old insitu population (blue solid) below [Fe/H]~=~$-1$, and by the old accreted
stars (red solid) above this value. We show the MW (M31) GCS in purple (magenta)
and we show the ratio of the simulated to the observed profiles in the middle
(bottom) panel. This mass excess can be thought of the `mass budget' that the
Auriga GC candidates can `afford to lose' due to a combination of smaller than
unity bound cluster formation efficiencies combined with a Hubble time of dynamical
evolution, while still producing a GC system with sufficient mass to be consistent
with the MW (M31) GCS. The cluster formation efficiency would have to linearly
decrease with decreasing metallicity for Auriga GC candidates to produce a population
of GC candidates that is consistent with the MW. For the GC candidates in M31
we find a constant mass excess up to $-0.9$, above which the
simulations produce a higher mass excess with increasing metallicity. If dynamical
evolution is not expected to more efficiently disrupt GCs of higher metallicity,
then we would find that the efficiency to form bound star clusters would have to
decrease with increasing metallicity.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMRgc_withRatios-trim}.png}
    \caption{
        Mass-weighted radial distribution of star particles in the Auriga
        simulations. We show the median value of all Auriga haloes for all
        stars (green dotted) and globular cluster candidates (i.e. stars with
        age $>$~10~Gyr; green solid). The latter sub set is further split up
        between stars that formed in-situ (blue solid), and those that were accreted
        (red solid). Shaded regions indicate the $1\sigma$ interval. The MW (M31)
        GCS is shown in purple (magenta). The middle (bottom) panel shows the
        ratio of the simulated mass to the mass in the MW (M31) GCS.
        \label{fig:Rgc}
    }
\end{figure}
Figure~\ref{fig:Rgc} shows the mass-weighted radial distribution of the
Auriga L4 haloes. We notice a subtle peak around $10$~kpc for all star
particles that is not present for the GC candidates, indicating that the
stellar disc is no longer present when applying the latter selection criterion.
Furthermore, we find that the dominant contribution to the total mass in GC
candidates changes from those formed insitu to the accreted population around
$10$~kpc. Again we show the mass excess of the simulations compared to the Milky
Way and Andromeda GCS. We find a decreasing mass excess with increasing radius
in the range $0.2$ to ${\sim}5$ kpc, followed by an increase attributed
to the accreted subpopulation. We further investigate a breakdown of the total mass
in Auriga GC candidates into bins of both metallicity and radius in the following
section.

@@

\section{Discussion}
% ``The Auriga Stellar Haloes: Connecting stellar population properties with
% accretion and merging history'' \citet{2018arXiv180407798M}

\label{sec:discussion}
\subsection{Metallicity distribution}
\label{sec:discussion_FeH}
Globular clusters are ${\sim}0.5$ dex more metal-poor than spheroid stars observed 
at the same radius for almost all galaxies \citep{1991ARA&A..29..543H}. Our 
selection function (age cut) does lower the mean metallicity by $0.5$ dex, but
we still find that the metallicity distributions of GC candidates in the Auriga
simulations are more metal-rich than the MW (M31) GCS. Although the (old) star
particles represent single stellar populations with a mass (resolution) consistent 
with that of GCs, they are in fact statistical tracers of the stellar population 
of the galaxy as a whole. Therefore only a (small) fraction of the star particles 
may represent plausible formation sites of GCs, whereas the majority represents 
(halo) field stars - the disk component effectively falls outside our selection 
of star particles due to the age cut.

In general, the colour (metallicity) distribution of most GC systems is bimodal 
with typical separating value [Fe/H]$\sim -1$ \citep{1985ApJ...293..424Z,
1999AJ....118.1526G,2001AJ....121.2974L,2006ApJ...639...95P}. Indeed, 
\citet[][p. 234]{1998gcs..book.....A} and \citet[][p. 38]{Harris2001} find that
the MW GCS has a bimodality [Fe/H] distribution: the latter fit a double Gaussian 
which peaks at [Fe/H] = $-1.59$ (metal-poor) and $-0.51$ (metal-rich) and 
dispersions of $0.34$ and $0.23$. Observations of GCs in M31, however, may be
best split into three distinct metallicity groups, one found at small radii with 
[Fe/H] $>-0.4$, one intermediate [Fe/H] group, and a dominant (metal-poor) group 
with [Fe/H] $< -1.5$ \citep{2016ApJ...824...42C}. The numerical simulation of
\citet{2017MNRAS.465.3622R} does yield a bimodal metallicity distribution where
the metal-poor population is dominated by accreted star particles and the metal-rich
population by insitu stars.

We find that none of the Auriga simulations produces a bimodal 
metallicity distribution for age-selected GC candidates. Interestingly, the 
cross-over point above (below) which the mass-weighted metallicity distribution
of GC candidates is dominated by those that have formed insitu (were accreted) 
does coincide with the separation between the metal-rich and metal-poor populations 
of GC systems at [Fe/H]~=~$-1$. Moreover, we do find that the mean metallicity
shifts when we split the GC candidates up according to birth location (accreted
or in-situ). In particular, the mean values of the old insitu GC candidates are 
roughly consistent with the metal-rich MW GCs. However, we also notice that a 
substantial number of simulations has similar mean values for all GC candidates, 
and the simulated insitu GC candidates have larger dispersions than the metal-rich 
GCs. Moreover, the offset between the mean of the metal-rich and metal-poor 
populations in the MW is $1$ dex, a factor $2-3$ larger than the offset that we 
find between the insitu and accreted populations. The Auriga simulations therefore
do not support the view that the metal-poor GCs could have formed in satellites
that have later been accreted whereas the metal-rich GC subpopulation has formed
insitu. With this statement, however, we do caution that \citet{2019MNRAS.486.3134K} 
suggests to reserve the `ex situ' classification for accretion after $z=2$, when
the central galaxy has formed and accretion unambigously contributes to the
radially extended halo GC population. In fact, our classification appears flawed
in Au4-1.

Finally, we note that \citet{2006ARA&A..44..193B} compares the number of metal-poor 
GCs to the stellar halo mass and find\footnote{the quantity $T$ is the number of 
GCs per $10^9$ M\Sun \, of galaxy stellar mass} $T^n_{\text{blue}} \sim 100$, 
while the number of metal-rich GCs compared to the bulge mass yields 
$T^n_{\text{red}} \sim 5$, and therefore conclude that the formation efficiency
of metal-poor GCs is twenty times higher than the metal-rich GCs with respect to 
field stars. We find that gradual linear increase in formation efficiency of GCs
with respect to field stars would be required with decreasing metallicity for
the GC candidates in the Auriga simulations to yield sufficient total mass to
be consistent with the Milky Way GCS.
